TAPIR: Threaded Application Programming on Intermittent Resources

### 2017-05-11 paper.tex
Added more related works

\usepackage{graphicx}
\DeclareGraphicsExtensions{.pdf,.jpg,.png}
\graphicspath{{./figures/} {./plots/}}

@@

%\author{
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
%% e-mail address with \email.
%\alignauthor Alice Security \\
%        \affaddr{Department of Computer Science}\\
%        \affaddr{University of Southern California}\\
%       \email{alice@example.edu}
%\alignauthor Bob Privacy \\
%    \affaddr{Networked Embedded Systems Group}\\
%    \affaddr{Swedish Institute of Computer Science}\\
%    \email{bob@example.se}
%}

@@

Operating system work\\
Want to do multiple things- i.e. federated energy \\
Dewdrop- energy aware task scheduling\\
TU delft guys...\\
Energy Align\\
TinyOS stuff in wireless sensor networks\\

@@

\section{Conclusion}
Multithreading in intermittence {\em is} a good idea!

>>>>

\usepackage{graphicx}
\DeclareGraphicsExtensions{.pdf,.jpg,.png}
\graphicspath{{./figs/} {./plots/}}

@@

%\author{

% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.

%\alignauthor Amanda Marano \\
%        \affaddr{Department of Electrical and Computer Engineering}\\
%        \affaddr{Carnegie Mellon University}\\
%       \email{amarano@andrew.cmu.edu}
%\alignauthor Emily Ruppel \\
%        \affaddr{Department of Electrical and Computer Engineering}\\
%        \affaddr{Carnegie Mellon University}\\
%       \email{eruppel@andrew.cmu.edu}
%\alignauthor Neil Ryan \\
%        \affaddr{Department of Electrical and Computer Engineering}\\
%        \affaddr{Carnegie Mellon University}\\
%       \email{nryan@andrew.cmu.edu}
%}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=0.99\columnwidth]{figs/listing}
  \caption{{\bf Example program for sensing and sending data}}
  \label{fig:copy}
\end{figure}

The wireless sensor networks community has explored multiple approaches for handling
multitasking on resource limited devices. The designs tend to provide a combination of
timer and event driven context switching as well as a simple programming interface.
TinyOS uses a simple FIFO scheduler to handle event based context switches~\cite{tiny}.
Nano-RK implements priority based preemptive multitasking where task priorities are
statically defined~\cite{nano}. Contiki uses proto-theads, stackless program threads, to
offer a model between nano-RK and tinyOS. The Contiki implements "cooperative
multithreading" such that events can trigger a context switch, but multithreading may also
be timer based~\cite{contiki}. The goal of multitasking interfaces in wireless sensor
networks is to provide a tradeoff between network lifetime and quality of service. This
differs from the intermittent programming model where the challenge is not system
lifetime, but system functionality based on energy availability.

@@

\section{Conclusion}
Multithreading in intermittence {\em is} a good idea!
\begin{figure}[ht]
  \centering
  \includegraphics[width=0.9\columnwidth]{figs/tapir}
\end{figure}
